MS_CNuptake.Rmd

### 2022-07-11 MS_CNuptake.Rmd
chec;

@@

length(na.omit(sitemean$obs_nmass))

###3. NRE model basing site-mean (lm)
NRE_climate <- read.csv("~/data/NRE_various/NRE_dataset.csv")
NRE_climate$nre_a <- log(NRE_climate$nre/(1-NRE_climate$nre))
NRE_climate$Tg_a <- NRE_climate$Tg
NRE_climate$vpd_a <- log(NRE_climate$vpd)
NRE_climate$PPFD_a <- log(NRE_climate$PPFD)
NRE_climate$ndep_a <- log(NRE_climate$ndep)
NRE_climate2 <- na.omit(NRE_climate[,c("nre_a","vpd_a","Tg_a","PPFD_a","ndep_a")])
stepwise_lm(NRE_climate2,"nre_a")[[1]]
nre_model <- lm(nre_a~Tg_a+vpd_a,data=NRE_climate2)
summary(nre_model)
r.squaredGLMM(nre_model)
length(na.omit(NRE_climate$nre_a))
#validation directly
NRE_climate$pred_nre <- (1/(1+exp(-(summary(nre_model)$coefficients[1,1] + summary(nre_model)$coefficients[2,1] *NRE_climate$Tg_a + 
                                      summary(nre_model)$coefficients[3,1] * NRE_climate$vpd_a))))

@@

#fig.2 validation
#plot_grid(p1,p2,p5,
#          p8,p9,p10,
#          p3,p4,p11,
#          p6,p12,p7, 
#          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)','(j)','(k)','(l)'),
#          ncol=3,label_x = 0.9,label_y=0.92,label_size = 25)+white
#ggsave(paste("~/data/output/newphy_fig2.jpg",sep=""),width = 24, height = 25)

#now, inputting all predictors
vcmax25_df <- as.data.frame(nc_to_df(read_nc_onefile(
  "~/data/nimpl_sofun_inputs/map/Final_ncfile/vcmax25.nc"),
  varnam = "vcmax25"))

@@

#plot_grid(g1,g2,g3,g4,g5,g6,
#          g7,g8,g9,g10,g11,g12,
#          g15,g16,g17,g18,
#          nrow=3,rel_widths = c(3/12, 1/12,3/12,1/12,3/12,1/12),
#          labels = c('(a)',' ','(b)',' ','(c)',' ',
#                     '(d)',' ','(e)',' ','(f)',' ',
#                     '(g)',' ','(h)',' '),label_size = 15)+white
#
#ggsave(paste("~/data/output/newphy_fig4_not_used.jpg",sep=""),width = 20, height = 10)

#figs2 representing all predictors
gg <- plot_map3(na.omit(CNrt[,c("lon","lat","myvar")]),varnam = "myvar",latmin = -65, latmax = 85,combine=FALSE)
d1 <- gg$ggmap +labs(title = "Soil C/N")+theme_grey(base_size = 15)+ white;d2 <- gg$gglegend+ white

@@

mean(abs((Nmin_statistical$Nmin-Nmin_statistical$ORCHICNP_fNup)/Nmin_statistical$Nmin),na.rm=TRUE) * 100
mean(abs((Nmin_statistical$Nmin-Nmin_statistical$ISAM_fNup)/Nmin_statistical$Nmin),na.rm=TRUE) * 100
mean(abs((Nmin_statistical$Nmin-Nmin_statistical$JSBACH_fNup)/Nmin_statistical$Nmin),na.rm=TRUE) * 100
mean(abs((Nmin_statistical$Nmin-Nmin_statistical$LPX_fNup)/Nmin_statistical$Nmin),na.rm=TRUE) * 100
mean(abs((Nmin_statistical$Nmin-Nmin_statistical$pred_nuptake)/Nmin_statistical$Nmin),na.rm=TRUE) * 100

#visreg

>>>>

    if (!identical(filnam, NA)) {
      ggsavex`x(filnam, width=5, height=5)
    }

@@

length(na.omit(sitemean$obs_nmass))
```

```{r setup, include=FALSE}
###3. NRE model basing site-mean (lm)
NRE_climate <- read.csv("~/data/NRE_various/NRE_dataset.csv")
NRE_climate$nre_a <- log(NRE_climate$nre/(1-NRE_climate$nre))
NRE_climate$Tg_a <- NRE_climate$Tg
NRE_climate$vpd_a <- log(NRE_climate$vpd)
NRE_climate$PPFD_a <- log(NRE_climate$PPFD)
NRE_climate$ndep_a <- log(NRE_climate$ndep)
NRE_climate2 <- na.omit(NRE_climate[,c("nre_a","vpd_a","Tg_a","PPFD_a","ndep_a")])
stepwise_lm(NRE_climate2,"nre_a")[[1]]
nre_model <- lm(nre_a~Tg_a+vpd_a,data=NRE_climate2)
summary(nre_model)
r.squaredGLMM(nre_model)
length(na.omit(NRE_climate$nre_a))
#validation directly
NRE_climate$pred_nre <- (1/(1+exp(-(summary(nre_model)$coefficients[1,1] + summary(nre_model)$coefficients[2,1] *NRE_climate$Tg_a + 
                                      summary(nre_model)$coefficients[3,1] * NRE_climate$vpd_a))))

@@

#fig.2 validation
#plot_grid(p1,p2,p5,
#          p8,p9,p10,
#          p3,p4,p11,
#          p6,p12,p7, 
#          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)','(j)','(k)','(l)'),
#          ncol=3,label_x = 0.9,label_y=0.92,label_size = 25)+white
#ggsave(paste("~/data/output/newphy_fig2.jpg",sep=""),width = 24, height = 25)
```

```{r setup, include=FALSE}
#now, inputting all predictors
vcmax25_df <- as.data.frame(nc_to_df(read_nc_onefile(
  "~/data/nimpl_sofun_inputs/map/Final_ncfile/vcmax25.nc"),
  varnam = "vcmax25"))

@@

#plot_grid(g1,g2,g3,g4,g5,g6,
#          g7,g8,g9,g10,g11,g12,
#          g15,g16,g17,g18,
#          nrow=3,rel_widths = c(3/12, 1/12,3/12,1/12,3/12,1/12),
#          labels = c('(a)',' ','(b)',' ','(c)',' ',
#                     '(d)',' ','(e)',' ','(f)',' ',
#                     '(g)',' ','(h)',' '),label_size = 15)+white
#
#ggsave(paste("~/data/output/newphy_fig4_not_used.jpg",sep=""),width = 20, height = 10)
```

```{r setup, include=FALSE}
#figs2 representing all predictors
gg <- plot_map3(na.omit(CNrt[,c("lon","lat","myvar")]),varnam = "myvar",latmin = -65, latmax = 85,combine=FALSE)
d1 <- gg$ggmap +labs(title = "Soil C/N")+theme_grey(base_size = 15)+ white;d2 <- gg$gglegend+ white

@@

mean(abs((Nmin_statistical$Nmin-Nmin_statistical$ORCHICNP_fNup)/Nmin_statistical$Nmin),na.rm=TRUE) * 100
mean(abs((Nmin_statistical$Nmin-Nmin_statistical$ISAM_fNup)/Nmin_statistical$Nmin),na.rm=TRUE) * 100
mean(abs((Nmin_statistical$Nmin-Nmin_statistical$JSBACH_fNup)/Nmin_statistical$Nmin),na.rm=TRUE) * 100
mean(abs((Nmin_statistical$Nmin-Nmin_statistical$LPX_fNup)/Nmin_statistical$Nmin),na.rm=TRUE) * 100
mean(abs((Nmin_statistical$Nmin-Nmin_statistical$pred_nuptake)/Nmin_statistical$Nmin),na.rm=TRUE) * 100
```

```{r setup, include=FALSE}
#visreg
